---
title: "Trip advisor scrapping for DC class"
output: html_notebook
---

This is a data collection assignment for CBA.

Submitted By:

Start Date: 17MAR2017

---

Assignment: The motive is to scrap tripadvisor.in website for any third tire indian city and obtain the following information:
- Name of the hotel
- URL of the hotel
- Address
- Price and saving
- Number of review and average rating
- Facilities provided by the hotel

---

Part 0: Installing the required packages

```{r}
suppressPackageStartupMessages({
  if (!require(rvest)) {install.packages("rvest")}; library(rvest)
  if (!require(stringr)) {install.packages("stringr")}; library(stringr)
  if (!require(dplyr)) {install.packages("dplyr")}; library(dplyr)
  if (!require(magrittr)) {install.packages("magrittr")}; library(magrittr)
}
)
```


Part 1: Getting the hotel name and URL from the page.

I am providing the input of the URL from Trip Advisor with the list of hotels for the city.
For this example, I am taking Vellore in Tamil Nadu to obtain the information.

```{r}
#saving the main URL of TA to this variable. This is essential because, when scrapping URL, the home URL of the page is not obtained
ta <- "https://www.tripadvisor.in"

#Appending the searched URL with the mail URL
ta.url <- paste(ta, "/Hotels-g1152780-Vellore_Vellore_District_Tamil_Nadu-Hotels.html", sep = "")

#Reading the page source of the URL
ta.url.content <- read_html(ta.url)

#reading the hotel name
hotel.name <- ta.url.content %>% html_nodes(".prominent") %>% html_text()

#Reading the URL of the hotel
hotel.url <- ta.url.content %>% html_nodes(".prominent") %>% html_attr("href")

#appending the URL of the hotel with the trip advisor home URL
hotel.url <- paste(ta, hotel.url, sep = "")
hotel.url

#creating a dataframe with all the available details
hotel.df <- data.frame(Name = hotel.name, Link = hotel.url)
hotel.df
```

Now I am going to try to extract all the details from just one Hotel's URL and then loop it in from the hotel.url created.

Part 2: Getting the information needed

---

Variable 1 = Hotel name from inside the page

```{r}
link <- "https://www.tripadvisor.in/Hotel_Review-g1162528-d1446668-Reviews-Monal_Resort-Rudra_Prayag_Rudraprayag_District_Uttarakhand.html"
one.hotel <- read_html(link)

hotel.name <- one.hotel %>% html_nodes("#HEADING") %>% html_text()
hotel.name
```

Variable 2 = Hotel address

```{r}
address <- one.hotel %>% html_nodes(".is-hidden-mobile.blEntry.address") %>% html_nodes(".detail") %>%  html_text() 
address
```

Variable 3 = Price of the hotel

```{r}
price <- one.hotel %>% html_nodes(".price") %>% html_text()
price
if (length(price) > 0) {
  price1 <- strsplit(price, "\u20b9")[[1]]
  typeof(price1)
}
price1
```

Now inside price there are various pries. Trying to get the actual price that shows for booking.
This is not easy to get, so I use four different methods from CSS selector's nodes to find if the price is contained in this element.

```{r}
#METHOD 1 FOR CHCKING PRICE
price.given <- one.hotel %>% html_nodes(".hasStrikeThrough .price") %>% html_text()
price.given1 <- strsplit(price.given, "\u20b9") %>% sapply("[[", 2) %>% str_replace_all("[[:punct:]]", "") %>% trimws(which = c("both"))

#METHOD 2 FOR CHECKING PRICE
if (length(price.given1) == 0) {
  price.given <- one.hotel %>% html_nodes(".hasStrikeThrough") %>% html_text()
price.given1 <- strsplit(price.given, "\u20b9") %>% sapply("[[", 2) %>% str_replace_all("[[:punct:]]", "") %>% trimws(which = c("both"))
}

#METHOD 3 FOR CHECKING PRICE
if (length(price.given1) == 0) {
  price.given <- one.hotel %>% html_nodes(".bb_price_text") %>% html_text()
price.given1 <- strsplit(price.given, "\u20b9") %>% sapply("[[", 2) %>% str_replace_all("[[:punct:]]", "") %>% trimws(which = c("both"))
}

#METHOD 4 FOR CHCKING PRICE
if (length(price.given1) == 0) {
  price.given <- one.hotel %>% html_nodes(".lowestPriceFlagPresent .price") %>% html_text()
price.given1 <- strsplit(price.given, "\u20b9") %>% sapply("[[", 2) %>% str_replace_all("[[:punct:]]", "") %>% trimws(which = c("both"))
}

price.given1
```

In few cases none of the methods return the price. For those cases we will use the price obtained from the page's first instance from the price variable.

```{r}
#METHOD 5 FOR CHCKING PRICE
if (length(price.given1) == 0) {
  price.given1 <- price1
}
```

Now in the next part, I try to find the actual price without any discount.
This is used to calculate savings.
In case if this is not available, then assigning price.given1 to it

```{r}
price.actual <- one.hotel %>% html_nodes(".xthrough_bad") %>% html_text()
price.actual1 <- strsplit(price.actual, "\u20b9") %>% sapply("[[", 2) %>% str_replace_all("[[:punct:]]", "") %>% trimws(which = c("both"))

if (length(price.actual1) == 0) {
  price.actual <- one.hotel %>% html_nodes(".xthrough") %>% html_text()
price.actual1 <- strsplit(price.actual, "\u20b9") %>% sapply("[[", 2) %>% str_replace_all("[[:punct:]]", "") %>% trimws(which = c("both"))
}

if (length(price.actual1) == 0) {
price.actual1 <- price.given1
}

price.actual1
```

Variable 4 = Saving

Subtracting actual price and the given price to obtain saving.

```{r}
#Function to extract only numeric part
numextract <- function(string){ 
  as.numeric( str_extract(string, "\\-*\\d+\\.*\\d*"))
} 

saving =numextract(  price.actual1) - numextract( price.given1)
saving
```

Variable 5 = Obtaining number of reviews and rating of the hotels

```{r}
no.of.reviews <- one.hotel %>% html_nodes(".reviews_header_count") %>% html_text()
if (length(no.of.reviews) == 0) {no.of.reviews <- "0"}
no.of.reviews1 <- numextract(no.of.reviews)

no.of.reviews1

rating <- one.hotel %>% html_nodes(".overallRating") %>% html_text() %>% numextract()
if (is.na(rating)) {rating <- 0}
rating
```

Variable 6 = Facilities

Obtaining all the Facilities and putting on the same string.

```{r}
facilities <- one.hotel %>% html_nodes(".detailListItem") %>% html_text()
facilities

fac = ""
for (i in facilities){
  fac = paste(fac, i, sep = ", ")
}

fac
```

Part 3: Creating a DF with all the data:

```{r}
this.hotel <- data.frame(Name = hotel.name
                      ,URL = link
                    ,Address = address
                      ,Actual_price = price.actual1
                      ,Offer_price = price.given1
                      ,Saving = saving
                      ,No_of_review = no.of.reviews1
                      ,Average_rating = rating
                      ,Facilities = fac)

this.hotel
```

Part 4: Creating an empty dataframe for the details:

```{r}
hotel <- data.frame(Name = character()
                      ,URL = character()
                    ,Address = character()
                      ,Actual_price = character()
                      ,Offer_price = character()
                      ,Saving = double()
                      ,No_of_review = double()
                      ,Average_rating = double()
                      ,Facilities = character())
```


Part 5: Itterating all the URL's data over and over and appending to hotel dataframe:

```{r}
for (links in hotel.url){
  one.hotel <- read_html(links)

hotel.name <- one.hotel %>% html_nodes("#HEADING") %>% html_text()

address <- one.hotel %>% html_nodes(".is-hidden-mobile.blEntry.address") %>% html_nodes(".detail") %>%  html_text() 
address

price <- one.hotel %>% html_nodes(".price") %>% html_text()
if (length(price) > 0) {
price1 <- strsplit(price, "\u20b9")[[1]]
typeof(price1)
}

#METHOD 1 FOR CHCKING PRICE
price.given <- one.hotel %>% html_nodes(".hasStrikeThrough .price") %>% html_text()
price.given1 <- strsplit(price.given, "\u20b9") %>% sapply("[[", 2) %>% str_replace_all("[[:punct:]]", "") %>% trimws(which = c("both"))

#METHOD 2 FOR CHCKING PRICE
if (length(price.given1) == 0) {
  price.given <- one.hotel %>% html_nodes(".hasStrikeThrough") %>% html_text()
price.given1 <- strsplit(price.given, "\u20b9") %>% sapply("[[", 2) %>% str_replace_all("[[:punct:]]", "") %>% trimws(which = c("both"))
}

#METHOD 3 FOR CHCKING PRICE
if (length(price.given1) == 0) {
  price.given <- one.hotel %>% html_nodes(".bb_price_text") %>% html_text()
price.given1 <- strsplit(price.given, "\u20b9") %>% sapply("[[", 2) %>% str_replace_all("[[:punct:]]", "") %>% trimws(which = c("both"))
}

#METHOD 4 FOR CHCKING PRICE
if (length(price.given1) == 0) {
  price.given <- one.hotel %>% html_nodes(".lowestPriceFlagPresent .price") %>% html_text()
price.given1 <- strsplit(price.given, "\u20b9") %>% sapply("[[", 2) %>% str_replace_all("[[:punct:]]", "") %>% trimws(which = c("both"))
}

#METHOD 5 FOR CHCKING PRICE
if (length(price.given1) == 0) {
  price.given1 <- price1
}

price.actual <- one.hotel %>% html_nodes(".xthrough_bad") %>% html_text()
price.actual1 <- strsplit(price.actual, "\u20b9") %>% sapply("[[", 2) %>% str_replace_all("[[:punct:]]", "") %>% trimws(which = c("both"))

if (length(price.actual1) == 0) {
  price.actual <- one.hotel %>% html_nodes(".xthrough") %>% html_text()
price.actual1 <- strsplit(price.actual, "\u20b9") %>% sapply("[[", 2) %>% str_replace_all("[[:punct:]]", "") %>% trimws(which = c("both"))
}

if (length(price.actual1) == 0) {
price.actual1 <- price.given1
}

numextract <- function(string){ 
  as.numeric( str_extract(string, "\\-*\\d+\\.*\\d*"))
} 

saving =numextract(  price.actual1) - numextract( price.given1)

no.of.reviews <- one.hotel %>% html_nodes(".reviews_header_count") %>% html_text()
if (length(no.of.reviews) == 0) {no.of.reviews <- "0"}
no.of.reviews1 <- numextract(no.of.reviews)

rating <- one.hotel %>% html_nodes(".overallRating") %>% html_text() %>% numextract()
if (is.na(rating)) {rating <- 0}

facilities <- one.hotel %>% html_nodes(".detailListItem") %>% html_text()
facilities

fac = ""
for (i in facilities){
  fac = paste(fac, i, sep = ", ")
}

fac

this.hotel <- data.frame(Name = hotel.name
                      ,URL = links
                    ,Address = address
                      ,Actual_price = price.actual1
                      ,Offer_price = price.given1
                      ,Saving = saving
                      ,No_of_review = no.of.reviews1
                      ,Average_rating = rating
                      ,Facilities = fac)

hotel<- rbind(hotel, this.hotel)
}
```

Finally: Here is hotel DF with all the data:

```{r}
print(hotel)
```


Please provide your feedback!
Thank you!